Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-23 analysis/paper/paper.Rmd
Clarify that this manuscript was not a part of the analysis

The second level is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or other long-term repository as provided by a library, Zenodo, FigShare, etc.
Fewer authors choose to follow this method, but in one instance that we found, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here.

>>>>

The second level is providing machine readable text files of the raw data and code in a public code repository such as GitHub, GitLab, but without a DOI or other long-term repository as provided by a library, Zenodo, FigShare, etc.
Fewer authors choose to follow this method, but in one instance that we found, which was not a part of this analysis, @Vogel2021 deposited Fastq files in the National Center of Biotechnology Information Sequence Read Archive (BioProject accession number PRJNA616021) and provided the scripts for analysis via a GitHub repository (<https://github.com/gmv23/pcap-gwas>) but we were unable to find a DOI that refers to these materials or a proper citation to properly cite them here.
